\propertitle

### 2019-07-08 maxNt_v5.tex
update

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-07-08T13:40:41+0200
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Maximum-entropy distributions for a 
  neuronal network\\ from subnetwork data%\\{\large ***}%
}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Maximum-entropy from sample data}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

\begin{figure}[!p]
\centering
\includegraphics[width=\linewidth]{_scripts/comparison_full.pdf}%
\\[3em]%
\includegraphics[width=\linewidth]{_scripts/comparison_marginals.pdf}%
\caption{***}
\label{fig:comparisons_marginals}
\end{figure}
%comparison_ME_sample_full_levels.nb
Does the application to the full-network lead to very different results
from the one to the sample? Figure~\ref{fig:comparisons_marginals} gives a
graphical answer in the case of the first data set. The upper plot shows
the maximum-entropy distributions for a full network of $10\,000$ neurons,
constructed from two moments (\textcolor{mygreen}{dashed green curve}) and
from four moments (\textcolor{myblue}{solid blue curve}). The lower plot
shows the maximum-entropy distributions for the sample (dashed curves),
from two moments (\textcolor{mygreen}{empty green triangles}) and from four
moments (\textcolor{mygreen}{empty blue squares}), and the distributions
obtained by marginalizing the full-network distribution to the sample size
(solid curves), from two moments (\textcolor{mygreen}{filled green
  triangles}) and from four moments (\textcolor{mygreen}{filled blue
  squares}). The measured frequency distribution (\textcolor{myred}{red
  circles}) is also shown. We note the following:
\begin{itemize}
\item The application to the full-network (upper plot) leads to two
  completely different distributions (even different number of modes);
  clearly the two statistics are not even approximately equivalent for
  inferential purposes.
\item The application to the sample leads to deceivingly similar
  distributions (empty triangles and empty squares), which can only be
  distinguished on a logarithmic scale. This could lead to the erroneous
  conclusion that the two statistics are approximately equivalent.
\item The difference between marginals from the full-network distribution
  and the distributions obtained at the sample level (filled vs empty
  markers) is larger than the difference between different statistics
  (triangles vs squares).
\item The marginals of the application to the full network are closer to
  the measured frequencies than the distributions obtained at the sample
  level (although this closeness is not a valid criterion for their
  goodness).
\end{itemize}
Therefore, the two maximum-entropy applications lead to different results,
and the application at the full-network level is clearly superior, leading
to a clearer distinction between the effect of considering different
statistics.

@@

in-depth discussion about underlying assumptions, derivation from
probability calculus, higher-order approximations beyond maxent and
"error bars" around the distributions
\begin{figure}[!p]
\centering
\includegraphics[width=\linewidth]{_scripts/MC_plot1000.pdf}%
\\[3em]%
\includegraphics[width=\linewidth]{_scripts/MC_samples1000.pdf}%
\caption{***}
\label{fig:comparisons_marginals}
\end{figure}
%mctests3.nb
%plot_mcfd_6mom_unif_afssd26_cok_tr_N1000_t50_L50_T0.333333333333333_s60000_a0

>>>>

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-07-08T16:40:48+0200
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Maximum-entropy distributions for a 
  neuronal network\\ from subnetwork data%\\{\large ***}%
}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Maximum-entropy from sample data}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

\begin{figure}[!p]
\centering
\includegraphics[width=\linewidth]{_scripts/comparison_full.pdf}%
\\[3em]%
\includegraphics[width=\linewidth]{_scripts/comparison_marginals.pdf}%
\caption{***}
\label{fig:comparisons_marginals}
\end{figure}
%comparison_ME_sample_full_levels.nb
Does the application to the full-network lead to very different results
from the one to the sample? Figure~\ref{fig:comparisons_marginals} gives a
graphical answer in the case of the first data set. The upper plot shows
the maximum-entropy distributions for a full network of $10\,000$ neurons,
constructed from two moments (\textcolor{mygreen}{dashed green curve}) and
from four moments (\textcolor{myblue}{solid blue curve}). The lower plot
shows the maximum-entropy distributions for the sample (empty markers),
from two moments (\textcolor{mygreen}{empty green triangles}) and from four
moments (\textcolor{myblue}{empty blue squares}), and the distributions
obtained by marginalizing the full-network distribution to the sample size
(filled markers), from two moments (\textcolor{mygreen}{filled green
  triangles}) and from four moments (\textcolor{myblue}{filled blue
  squares}). The measured frequency distribution (\textcolor{myred}{red
  circles}) is also shown. We note the following:
\begin{itemize}
\item The application to the full-network (upper plot) leads to two
  completely different distributions (even different number of modes);
  clearly the two statistics are not even approximately equivalent for
  inferential purposes.
\item The application to the sample leads to deceivingly similar
  distributions (empty triangles and empty squares), which can only be
  distinguished on a logarithmic scale. This could lead to the erroneous
  conclusion that the two statistics are approximately equivalent.
\item The difference between marginals from the full-network distribution
  and the distributions obtained at the sample level (filled vs empty
  markers) is larger than the difference between different statistics
  (triangles vs squares).
\item The marginals of the application to the full network are closer to
  the measured frequencies than the distributions obtained at the sample
  level (although this closeness is not a valid criterion for their
  goodness).
\end{itemize}
Therefore, the two maximum-entropy applications lead to different results,
and the application at the full-network level is clearly superior, leading
to a clearer distinction between the effect of considering different
statistics.

@@

***in-depth discussion about underlying assumptions, derivation from
probability calculus, higher-order approximations beyond maxent and
"error bars" around the distributions

***We can ask about probability of bimodality etc

\begin{figure}[!p]
\centering
\includegraphics[width=\linewidth]{_scripts/MC_plot1000.pdf}%
\\[3em]%
\includegraphics[width=\linewidth]{_scripts/MC_samples1000.pdf}%
\caption{***}
\label{fig:comparisons_marginals}
\end{figure}
%mctests3.nb
%plot_mcfd_6mom_unif_afssd26_cok_tr_N1000_t50_L50_T0.333333333333333_s60000_a0
